README

### 2014-06-20 README.Rmd
Added plot
More toying with README plot.

---
title: "README"
output: html_document
---

SpatialEpi: Methods and Data for Spatial Epidemiology
===========================================
We load the data and convert the coordinate system from latitude/longitude to a 
grid-based system.  
```{r}
require(SpatialEpi)
data(NYleukemia)
map <- NYleukemia$spatial.polygon
centroids <- latlong2grid(NYleukemia$geo[, 2:3])
population <- NYleukemia$data$population
cases <- NYleukemia$data$cases
```

@@

We plot the incidence of leukemia for each census tract.  
```{r, fig.height=8, fig.width=8}
plotmap(cases/population, map, log=TRUE, nclr=5)
points(grid2latlong(centroids), pch=4)
```

>>>>

---
output:
  html_document: default
---

SpatialEpi
===========================================
Methods and Data for Spatial Epidemiology
-------------------------------------------
We load the data and convert the coordinate system from latitude/longitude to a 
grid-based system.  
```{r}
require(SpatialEpi)
data(NYleukemia)
map <- NYleukemia$spatial.polygon
centroids <- latlong2grid(NYleukemia$geo[, 2:3])
population <- NYleukemia$data$population
cases <- NYleukemia$data$cases
```

@@

We plot the incidence of leukemia for each census tract.  
```{r, fig.height=8, fig.width=8, fig.path='./figure/'}
plotmap(cases/population, map, log=TRUE, nclr=5)
points(grid2latlong(centroids), pch=4)
```
